---
title: "A Brief Cross-Cultural Study on the Importance of Relationships"
author: "Miles Anim-Appiah"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I will be using YES Lab data pertaining to function weakening actions that inform the relational dynamics in a series of hypothetical relationships.

How variable is relationship importance within cultures? Across cultures? Individuals from American and Chinese samples rated the importance of various relationships from 1 (not important) to 100 (very important)

1. isolate values for relationship importance for each subject
2. 2x2 anova, output variable relationship importance, predictor variables are relationship type and culture, examine main effect of relationship, culture
3. posthoc t-test, examine differences in relationship importance between cultures
4. bar graph, x-axis relationship, y-axis relationship importance, bars colored by culture


```{r}
library(dplyr)
library(tidyverse)
data<-read.csv("df.all_long_usacn.csv")

## 0.
data$relationship <- gsub("acquaintances", "acq", data$relationship, ignore.case = TRUE)

## 1.
dataRelImp<-data[,c(1:3,10)]
isoRelImp <- dataRelImp %>%
  distinct(subject, relationship_imp, relationship, culture, .keep_all = TRUE)

## 2.
anova_isoRelImp<-aov(relationship_imp~relationship*culture,data=isoRelImp)
summary(anova_isoRelImp)

## 3.
library(emmeans)
posthoc<-emmeans(anova_isoRelImp,pairwise~culture|relationship)
summary(posthoc)

## 4. 
graphRelImp<-ggplot(data=isoRelImp,
                aes(x=relationship,
                    y=relationship_imp,
                    fill= relationship))

```




